Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-23 paper/manuscript.tex
H3 numbering subsection of Methods

\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Figure}]{suppfigure}
\renewcommand{\thesuppfigure}{S\arabic{suppfigure}}
\DeclareFloatingEnvironment[name={Table}]{supptable}
\renewcommand{\thesupptable}{S\arabic{supptable}}

@@

We also estimated the overall fraction of virions surviving each antibody selection.
These fractions are denoted by $\gamma$ in this paper.
The average of these fractions across libraries are reported in Figure~\ref{fig:neutcurves}, and the values for each individual replicate are in Table~\ref{supptab:fracsurvive}.
\comment{I AM HERE}
we made duplicate 10-fold serial dilutions of each of the virus libraries to use as a standard curve of infectivity. 
qRT-PCR of the standard curves were performed as previously described in~\cite{doud2017complete} using qPCR primers for WSN influenza nucleoprotein (NP) to quantify viral infectivity and primers for canine GAPDH to correct for RNA amounts.
Next, we fit a linear regression of the log(infectious dose) versus the mean difference in qPCR Ct values between NP and GAPDH to estimate the total library fraction infectivity after antibody selection.

@@

\subsection*{H3 sequence numbering}
Unless otherwise indicated, all residues are numbered in H3 numbering in this paper, with the signal peptide in negative numbers, the HA1 subunit as plain numbers, and the HA2 subunit denoted with "(HA2)". We converted the sequential residue numbers into H3 numbering by running the Python script available on \url{https://github.com/jbloomlab/HA_numbering}. In this script, we used MUSCLE to align the WSN/1933 H1 HA sequence to the 4HMG pdb sequence for the A/Aichi/2/1968 H3 HA \comment{cite Weis1990JMB}, which allowed us to convert from the sequential numbering to the H3 numbering scheme.

@@

\begin{supptable}
\centering
\begin{tabular}{cccc}
antibody &  concentration ($\mu$g/ml) &  replicate &  fraction surviving \\
\hline
FI6v3 &            0.1 &  1a &             0.01662 \\
 FI6v3 &            0.1 &  1b &             0.01390 \\
FI6v3 &            0.2 &  1a &             0.00465 \\
FI6v3 &            0.2 &  1b &             0.00345 \\
FI6v3 &            0.1 &  2 &             0.02322 \\
FI6v3 &            0.2 &  2 &             0.00278 \\
FI6v3 &            0.1 &  3 &             0.00903 \\
FI6v3 &            0.2 &  3 &             0.00144 \\
S139/1 &          100.0 &  1 &             0.02490 \\
S139/1 &          200.0 &  1 &             0.01470 \\
S139/1 &          300.0 &  1 &             0.01270 \\
S139/1 &          100.0 &  2 &             0.02190 \\
S139/1 &          200.0 &  2 &             0.01720 \\
S139/1 &          300.0 &  2 &             0.00854 \\
S139/1 &          100.0 &  3 &             0.05180 \\
S139/1 &          200.0 &  3 &             0.04060 \\
S139/1 &          300.0 &  3 &             0.03750 \\
C179 &            1.0 &    1a &             0.00941 \\
C179 &            1.0 &    1b &             0.00890 \\
C179 &            1.0 &    1c &             0.00960 \\
C179 &            2.5 &    1 &             0.00450 \\
C179 &            1.0 &    2 &             0.00554 \\
C179 &            2.5 &    2 &             0.00198 \\
C179 &            1.0 &    3 &             0.00256 \\
C179 &            2.5 &    3 &             0.00100 \\
\end{tabular}
\caption{\label{supptab:fracsurvive}
The total fraction of virions surviving each antibody treatment at each concentration as estimated by qPCR.
These are the quantities referred to as $\gamma$.
This table shows the values for the broad antibodies; values for the narrow H17-L17, H17-L10, and H17-L7 antibodies are reported in \citet{doud2017complete}.
}
\end{supptable}

>>>>

\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Figure}]{suppfigure}
\renewcommand{\thesuppfigure}{S\arabic{suppfigure}}
\DeclareFloatingEnvironment[name={Table}]{supptable}
\renewcommand{\thesupptable}{S\arabic{supptable}}
\DeclareFloatingEnvironment[name={File}]{suppfile}
\renewcommand{\thesuppfile}{S\arabic{suppfile}}

@@

@@

\subsection*{H3 sequence numbering}
Unless otherwise indicated, all residues are numbered in the H3 numbering scheme, with the signal peptide in negative numbers, the HA1 subunit as plain numbers, and the HA2 subunit denoted with ``(HA2)''. 
The conversion between sequential numbering of the A/WSN/1933 HA and the H3 numbering scheme was performed using the Python script available at \url{https://github.com/jbloomlab/HA_numbering}.
File~\ref{suppfile:HAnumbering} gives the numbering conversion.

We also estimated the overall fraction of virions surviving each antibody selection.
These fractions are denoted by $\gamma$ in this paper.
The average of these fractions across libraries are reported in Figure~\ref{fig:neutcurves}, and the values for each individual replicate are in Table~\ref{supptab:fracsurvive}.
The fractions were estimated using qPCR against the viral NP and canine GAPDH as described in \citet{doud2017complete}.
Briefly, we made duplicate 10-fold serial dilutions of each of the virus libraries to use as a standard curve.
We also performed qPCR on the cells infected with the virus-antibody mix.
To estimate the fractions, we used linear regression to fit a line relating logarithm of the viral infectious dose in the standard curve to the difference in Ct values between NP and GAPDH, and then interpolated the fraction surviving for each selection from this regression.

@@

\begin{supptable}
\centering
\begin{tabular}{cccc}
antibody &  concentration ($\mu$g/ml) &  replicate &  fraction surviving \\
\hline
FI6v3 &            0.1 &  1a &             0.01662 \\
 FI6v3 &            0.1 &  1b &             0.01390 \\
FI6v3 &            0.2 &  1a &             0.00465 \\
FI6v3 &            0.2 &  1b &             0.00345 \\
FI6v3 &            0.1 &  2 &             0.02322 \\
FI6v3 &            0.2 &  2 &             0.00278 \\
FI6v3 &            0.1 &  3 &             0.00903 \\
FI6v3 &            0.2 &  3 &             0.00144 \\
S139/1 &          100.0 &  1 &             0.02490 \\
S139/1 &          200.0 &  1 &             0.01470 \\
S139/1 &          300.0 &  1 &             0.01270 \\
S139/1 &          100.0 &  2 &             0.02190 \\
S139/1 &          200.0 &  2 &             0.01720 \\
S139/1 &          300.0 &  2 &             0.00854 \\
S139/1 &          100.0 &  3 &             0.05180 \\
S139/1 &          200.0 &  3 &             0.04060 \\
S139/1 &          300.0 &  3 &             0.03750 \\
C179 &            1.0 &    1a &             0.00941 \\
C179 &            1.0 &    1b &             0.00890 \\
C179 &            1.0 &    1c &             0.00960 \\
C179 &            2.5 &    1 &             0.00450 \\
C179 &            1.0 &    2 &             0.00554 \\
C179 &            2.5 &    2 &             0.00198 \\
C179 &            1.0 &    3 &             0.00256 \\
C179 &            2.5 &    3 &             0.00100 \\
\end{tabular}
\caption{\label{supptab:fracsurvive}
{\bf The total fraction of virions surviving each antibody treatment at each concentration as estimated by qPCR.}
These are the quantities referred to as $\gamma$.
This table shows the values for the broad antibodies; values for the narrow H17-L17, H17-L10, and H17-L7 antibodies are reported in \citet{doud2017complete}.
}
\end{supptable}
\clearpage

\begin{suppfile}
\caption{\label{suppfile:HAnumbering}
{\bf Conversion from sequential numbering of the A/WSN/1933 HA to H3 numbering.}
In this CSV file, the \emph{original} column gives the residue number in sequential (1, 2, ...) numbering of the A/WSN/1933 HA, and the \emph{new} column gives the residue number in H3 numbering.
}
\end{suppfile}
